Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-09-01 ms/main.tex
formatting

These conditions are illustrated in \autoref{fig:results2}b-c.
Note that cooperation and defection can coexist stably if there is horizontal bias for defection and the cost of cooperation is large but not too large. The recursion dynamic for this case is illustrated in \autoref{fig:coexistence_without_oblique}.

@@

% in gamma
\begin{enumerate}
\item \emph{Fixation of cooperation}: 
	if \emph{(i)} $T=T_A=T_B$ and $c < b\cdot \frac{\alpha T}{1-T}$; or
	if \emph{(ii)} $T_A>T_B$ and $0<\beta_3$; or 
	if \emph{(iii)} $T_A<T_B$ and $\beta_1<\beta_3$.
\item \emph{Fixation of the defection}: 
	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \frac{\alpha T}{1-T}$; or 
	if \emph{(v)} $T_A>T_B$ and $\beta_1<\beta_3<0$; or 
	if \emph{(vi)} $T_A<T_B$ and $\beta_3<0$.
\item \emph{Coexistence of both phenotypes at $\hat{p}^*$}: 
  if \emph{(viia)} $T_A < T_B$ and $v<\hat{v}$ and $c<\hat{\gamma_1}$ and $c<\hat{\gamma_2}$; or
  if \emph{(viib)} $T_A < T_B$ and $v>\hat{v}$ and $c<\hat{\gamma_1}$ and $c>\hat{\gamma_2}$. %$0<\beta_3<\beta_1$.
\item \emph{Fixation of either phenotype depending on initial frequency}:
  if \emph{(viii)}  $T_A>T_B$ and $c > \hat{\gamma_2}$ and $c > \hat{\gamma_1}$ and $v>\hat{v}$.
\end{enumerate}

>>>>

These conditions are illustrated in \autoref{fig:results2}.
Note that cooperation and defection can coexist stably if there is horizontal bias for defection and the cost of cooperation is large but not too large. The recursion dynamic for this case is illustrated in \autoref{fig:coexistence_without_oblique}.

@@

% in gamma
\begin{enumerate}
\item \emph{Fixation of cooperation}: 
	if \emph{(i)} $T=T_A=T_B$ and $c < b\cdot \alpha \frac{T}{1-T}$; or
	if \emph{(ii)} $T_A>T_B$ and $c < \hat\gamma_1$; or 
	if \emph{(iiia)} $T_A<T_B$ and $v>\hat v$ and $c < \hat\gamma_2$; or
	if \emph{(iiib)} $T_A<T_B$ and $v<\hat v$ and $\hat\gamma_2 < c$.
\item \emph{Fixation of the defection}: 
	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \alpha \frac{T}{1-T}$; or 
  if \emph{(v)} $T_A>T_B$ and $\hat\gamma_1 < c < \hat\gamma_2$; or 
	if \emph{(vi)} $T_A<T_B$ and $\hat\gamma_1 < c$.
\item \emph{Coexistence of both phenotypes at $\hat{p}^*$}: 
  if \emph{(viia)} $T_A < T_B$ and $v<\hat{v}$ and $c<\hat\gamma_1$ and $c<\hat\gamma_2$; or
  if \emph{(viib)} $T_A < T_B$ and $v>\hat{v}$ and $c<\hat\gamma_1$ and $\hat\gamma_2 < c$. %$0<\beta_3<\beta_1$.
\item \emph{Fixation of either phenotype depending on initial frequency}:
  if \emph{(viii)}  $T_A>T_B$ and $\hat\gamma_2 < c$ and $\hat\gamma_1 < c$ and $v>\hat{v}$.
\end{enumerate}
